### 2023-03-15 paper/main.tex
first two sections completed for paper

\newpage    
\section{Application Benefits}
\subsection{What are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
\linebreak
Our application is a simple tool for conducting self-administered surveys. Our users can log into their profiles to view customer feedback to improve their businesses. QR codes can be generated for wide distribution and quick access. SurveyMonkey (\url{https://www.surveymonkey.com/}) and QuestionPro (\url{https://www.questionpro.com/}) are comparable existing systems. Some benefits of our application are that the users can received unlimited number of responses for their surveys without cost and all features to create the surveys are free as well. Our application does not have many templates and complicated tools that may negatively impact loading time. Respondents do not need to create an account to respond to surveys. 
\hfill \break

\subsubsection*{Survey Monkey}

@@

Survey Monkey's website is very overwhelming to look at on first glance, but after a bit of digging you are able to find a bit of information on the packages available. In the past, they have had a pretty large amount of features for free users, but now their free package is very limited. Currently, their free package only allows for unlimited surveys, but with a restriction of 10 questions each, and only allows for a limited amount of responses. This means that if you want to get information with a large group of people, you would have to create multiples of the same surveys and compile the data together manually.

\hfill \break
\subsubsection*{QuestionPro}

@@

\textbf{Feedback Gatherer}
\begin{enumerate}
   \item \textbf{Register:} Feedback gatherer creates an account by entering the required information
   \item \textbf{Create Survey:} Feedback gatherer creates a survey by entering questions and selecting type of responses
   \item \textbf{View QR Code:} Feedback gatherer views the generated QR code for the survey
   \item \textbf{Delete Survey:} Feedback gatherer deletes a survey that is no longer required
   \item \textbf{View Statistics and Responses:} Feedback gatherer views statistics and responses of a selected survey
\end{enumerate}
\newline 
\hfill \break

\textbf{Respondent}
\begin{enumerate}
   \item \textbf{Scan QR Code:} Respondent scans the QR code to view the survey
   \item \textbf{Enter Responses:} Respondent enters responses to the survey questions
   \item \textbf{Submit Response:} Respondent submits responses to the survey questions
\end{enumerate}

>>>>

\newpage    
\section{Application Benefits}
\subsection{What are the benefits of your application when compared to existing systems. Choose two systems only and include their references (2 pages).}
\linebreak
Our application is a simple tool for conducting self-administered surveys. Our users can log into their profiles to view customer feedback to improve their businesses. QR codes can be generated for wide distribution and quick access. SurveyMonkey (\url{https://www.surveymonkey.com/}) and QuestionPro (\url{https://www.questionpro.com/}) are comparable existing systems. Some benefits of our application are that the users can received unlimited number of responses for their surveys without cost and all features to create the surveys are free as well. Our application does not have many templates and complicated tools that may negatively impact loading time. Respondents do not need to create an account to respond to surveys.

\hfill

\subsubsection*{Survey Monkey}\hfill

@@

Survey Monkey's website is very overwhelming to look at on first glance, but after a bit of digging you are able to find a bit of information on the packages available. In the past, they have had a pretty large amount of features for free users, but now their free package is very limited. Currently, their free package only allows for unlimited surveys, but with a restriction of 10 questions each, and only allows for a limited amount of responses. This means that if you want to get information with a large group of people, you would have to create multiples of the same surveys and compile the data together manually.
\newline

Overall, SurveyMonkey is a good tool for users who want to create surveys quickly and easily, but it may not be the best fit for people who want more expansive options for length of survey, and ability to view feedback. The limited free plan and cost may also be a reason for people to choose an alternative.

\break
\subsubsection*{QuestionPro}\hfill

QuestionPro, similar to Survey Monkey, has many different options depending on the customer and type of data they want to collect. It has many of the same options as Survey Monkey has when it comes to questions type, but seems like it's list of features might be more expansive.
\newline

QuestionPro has a very similar home page to Survey Monkey, but made it easier to find the differences between their packages available. This site has many more features available for free users than Survey Monkey, but still has a limit to the amount of questions and responses unless you pay. Rather than limiting to 10 question per survey, QuestionPro allows free users to have up to 100 questions per survey with up to 300 responses which is a very large increase in comparison to Survey Monkey.
\newline

QuestionPro is definitely a powerful tool for creating surveys online, but may be confusing for users with limited technology experiences. The cost for full access is also a restriction for some, but in comparison to Survey Monkey, the free version includes a much larger amount of features and usability.
\newline

Both of these other platforms for similar survey creation to ours lock many features behind a paywall. Our goal to create a very simple survey platform eliminates the confusion from having too many options or limited response allowances to make it more user friendly. We also only have a free option available for all users, so no features are hidden behind a paywall, allowing everyone to have the same experience while using it.

@@

\textbf{Feedback Gatherer}
\begin{enumerate}
   \item \textbf{Register:} Feedback gatherer creates an account by entering the required information. 
   \item \textbf{Create Survey:} Feedback gatherer creates a survey by entering questions and selecting type of responses.
   \item \textbf{View QR Code:} Feedback gatherer views the generated QR code for the survey.
   \item \textbf{Delete Survey:} Feedback gatherer deletes a survey that is no longer required.
   \item \textbf{View Statistics and Responses:} Feedback gatherer views statistics and responses of a selected survey.
\end{enumerate}

\newline 
\hfill \break

\textbf{Respondent}
\begin{enumerate}
   \item \textbf{Scan QR Code:} Respondent scans the QR code to view the survey.
   \item \textbf{Enter Responses:} Respondent enters responses to the survey questions.
   \item \textbf{Submit Response:} Respondent submits responses to the survey questions.
\end{enumerate}
